### 2020-12-11 Thesis-Chapter3-PolicyMaking.tex
Editorial improvements

Cybersecurity law scholar Alan Rozenshtein argues at length for treating \ac{encryption} and \ac{EA} as a
\ac{wicked-prob} \cite{rozenshtein_wicked_2018}. He divides the root issues into three categories. First, there is
disagreement on what the goals should be (and even basic premises). Sides do not agree on whether things are ``going
dark'' or we're in the ``golden age for surveillance'' or how much to value competing notions of security. Second,
information is ``uncertain and diffuse.'' There are insufficient statistics on encryption's effect on investigations.
Though the consensus is that we are not presently capable of acceptably secure \ac{EA}, that is not certain to always be
the case, especially as the area is under-researched. Third, that the problem cannot be definitively solved. Evolving
values and technology mean that the subject is always up for renegotiation.

\Ac{encryption} technology is particularly sensitive to the irreversible effects of policy implementation. Technology
deployments have long tails, and attackers have the ability to record and store data for later analysis. In one
investigation, Australian authorities cracked a cold case based on evidence acquired from a mobile device that they
cracked five years after it was seized \cite{evans_arrests_2020}. Lawful authorities wouldn't be the only ones to
benefit from a policy miscalculation that could negatively impact security for a very long time.

@@

Embracing reality is the first step to dealing with it \cite{baker_2019}. We have by now embraced the reality of
\acp{wicked-prob}. The next two sections investigate strategies for dealing with it.

@@

The \ac{classical-method} \cite{feeley_judicial_2000} (also known as ``the modern-classical model of planning''
\cite{rittel_dilemmas_1973}, ``the rational-comprehensive method'' \cite{lindblom_muddling_1959}, ``traditional policy
analysis'' \cite{rozenshtein_wicked_2018}, or ``linear thinking'' \cite{commission_tackling_2018}) has already been
introduced. It is the reason-based method that functions by setting goals, identifying problems, evaluating
alternatives, implementing solutions, and analyzing outcomes in order to correct errors. \myfig{fig-classical-method}
illustrates this approach in the context of encryption and \ac{EA}. It has a purely linear flow from problem to solution
except for the ``refinement'' step, in which the method analyzes outcomes and corrects errors. However, it is important
to note that refinement is always in-kind---it represents a reinforcement, as opposed to a reassessment, of the chosen
solution.

@@

\Ac{incrementalism} is an intuitive and iterative approach posed as an alternative to the \ac{classical-method}.
\Ac{incrementalism} as a policymaking strategy is often referred to as ``\ac{muddling-through}'' after political
scientist Charles Lindblom's classic paper defining and defending the approach \cite{lindblom_muddling_1959}. Written
before Rittel developed the idea of ``\acp{wicked-prob},'' Lindblom nonetheless identified many of the same shortcomings
of the classical method and sought to formalize the process policymakers were already often using.

Lindblom's process of ``\ac{muddling-through}'' operates by taking successive steps chosen through comparative analysis.
The alternatives selected for comparison are defined relative to the status quo and are close enough to one another to
be able to be analyzed on the margin. This is done first out of practical necessity, due to our inability to rationally
predict policy outcomes, and second out of political realism, as non-incremental changes are usually politically
impossible to impose in a democratic system \cite{lindblom_muddling_1959}. The formality of the process varies;
policymakers may use this method consciously, with considerable comparative analysis, or unconsciously, led by
intuition. \myfig{fig-muddling-through} illustrates this method.

@@

\Ac{incrementalism} has several advantages over the \ac{classical-method} for handling \acp{wicked-prob}. It is rooted
in realism about the limits of rational analysis. It accepts that the problem will not be conclusively solved,
emphasizing iteration (``Policy is not made once and for all; it is made and re-made endlessly. Policy-making is a
process of successive approximation to some desired objectives in which what is desired itself continues to change under
reconsideration.'' \cite{lindblom_muddling_1959}). Most importantly, it eschews the linear
problem-definition--alternatives-analysis steps out of respect that this is, indeed, impossible. Lindblom argues at
length that policy ends and means are interlinked, eventually concluding:

@@

Despite its strengths, \ac{incrementalism} also has weaknesses in its ability to address \acp{wicked-prob}. Its main
weakness is the absence of high level strategic analysis. Incrementalism is incapable of drastic change, which is
sometimes necessary. By Lindblom's admission, it lacks a safeguard for consideration of all relevant values and may
``overlook excellent policies for no other reason than that they are not suggested by the chain of successive policy
steps leading up to the present'' \cite{lindblom_muddling_1959}. Analysis based only on one present ``status quo'' to
the next can result in messy policy that none are particularly fond of---``As Lindblom's sobriquet suggests, it often
[leads] to a considerable muddle'' \cite{feeley_judicial_2000}. Application of the \acl{CFAA} is one such muddle
\cite{wolff_computer_2016}.

Unfortunately, one cannot simply expand the strategic view of the incrementalist method by allowing it to look further
into the past than the present status quo. Simplifying analysis by limiting it to marginal differences to a given
baseline is at the heart of \ac{incrementalism}. If one tries to be a ``strategic incrementalist'' by looking into the
past, they still have to choose a baseline from which to perform analysis. This approach is susceptible to two
weaknesses in baseline-based reasoning that Rozenshtein describes in his analysis of \ac{EA} as a \ac{wicked-prob}
\cite{rozenshtein_wicked_2018}. First, the choice of baseline is arbitrary, yet heavily colors analysis:

@@

Let us define one strategy for handling \ac{wicked-prob} as corralling it back into the classes of problems we are
better at dealing with. That means breaking it into tame subproblems and developing agreeable strategies for its
irreducibly wicked elements. Once that is done, we can rationally analyze and increment our way to victory. There is no
handbook for how to do this, but several sources offer advice.

@@

Easy answers, or any solutions that artificially tame the problem, will not bring the matter under control. While by
definition there is no step that will truly solve the problem, easy answers deliberately emphasize one value to the
exclusion of others. This leads to chaos in those neglected areas. Solutions based on easy answers produce unintended
consequences because they ignore the root issues \cite{commission_tackling_2018}.

@@

% TODO:
% Prof. Engelsma
% - A big part of the "solution" is getting people together
% - My thesis seems aimed at tech people to get them to understand and judge threats
% - How can I take this accessible and bridge the gap for policymakers?

@@

The failures of the \ac{classical-method} and \ac{incrementalism} reveal that we must be able to think strategically
while respecting the non-linear nature of \acp{wicked-prob}. One way to use the high level, holistic view of the
classical approach while intertwining the problem definition and analysis steps as in the incrementalist approach. In
practice, this means that the collective understanding of the problem and potential solutions must co-evolve. As Rittel
puts it, ``The systems-approach `of the first generation' [i.e., classical analysis] is inadequate for dealing with
wicked-problems. Approaches of the `second generation' should be based on a model of planning as an argumentative
process in the course of which an image of the problem and of the solution emerges gradually among the participants, as
a product of incessant judgment, subjected to critical argument'' \cite{rittel_dilemmas_1973}.

@@

We know that proposals cannot be comprehensively evaluated before or even after implementation, and that each action (or
decision not to act) has irreversible effects. \Ac{incrementalism} is the decision making model to follow here, as it is
inherently responsive to unpredictable changes in the environment. Proposals must therefore be agile. All decisions
involve unknowns, but risk- and uncertainty-management strategies can optimize the expected outcome and maximize the
worst outcome \cite{sunstein_beyond_2015}.

@@

Focusing on concrete proposals follows partially from the previous suggestion---problem definition and analysis are
combined precisely because the problem definition depends on the nature of proposed solutions. But this advice deserves
emphasis for another reason: consensus is easier to build around concrete proposals. While debate rages in the abstract,
groups are bound to disagree due to their conflicting values and priorities. However, Lindblom writes encouragingly
about ``the ease with which individuals of different ideologies often can agree on concrete policy'' in an example
about congressional compromise. He goes on to say, ``Labor mediators report a similar phenomenon: the contestants cannot
agree on criteria for settling their disputes but can agree on specific proposals. Similarly, when one administrator's
objective turns out to be another's means, they often can agree on policy'' \cite{lindblom_muddling_1959}.

@@

The discussion above describes the inability of well-established methods of policymaking to address \acp{wicked-prob}
and properties a better method would have. Here, I propose a modified \acs{OODAloop} as an alternative policymaking
model.

@@

The \ac{OODAloop} serves well as a model for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action; however, it also emphasizes \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking does not share the pace of real-time combat, this metaphor holds true in other ways.
One is facing an unpredictable opponent in a dynamic environment in which every action counts. We cannot overpower
\acp{wicked-prob} through force of reason, but perhaps we can through speed and agility.

The OODA Loop does need one modification in order to suit wicked problems. Because the problem definition step and
analysis step depend on one another, they should be unified. This is Rittel's ``argumentative process in the course of
which an image of the problem and of the solution emerges gradually'' \cite{rittel_dilemmas_1973}, illustrated in
\myfig{fig-policy-ooda-loop} as a cycle of ``collaborative debate'' between observation and orientation. The modified
\ac{OODAloop} incorporates each of the lessons from \mysec{sec-policy-lessons}.

@@

Traditional policymaking typically follows either a rational approach rooted in the scientific method, aiming to be
thorough and complete, or an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have strengths, but neither is suited to the complex and controversial
nature of so-called ``\acp{wicked-prob}.'' The strategy proposed here relies on the goodwill participation of all
parties, who engage in ongoing research and debate that rejects easy answers, encourages flexible risk-based solutions,
and crystallizes discussion around specific proposals. The result of a single iteration is an imperfect step forward
based on implementing a particular proposal. The result of many iterations is the breakdown of the problem into
subproblems---some tame and inevitably some still wicked. The tame subproblems can be addressed with the
\ac{classical-method}, and the wicked subproblems, by now restrained under a sound and agreeable strategy, can be
addressed with \ac{incrementalism}.

% TODO: do I need this explanation?

This process is demonstrated in \myfig{fig-policy-ooda-process}. An out-of-control problem (the large storm) is
confronted in this diagram. Several iterations of the \ac{OODAloop} gradually diminish its size. This is achieved by
spinning out tame problems (puzzle pieces) addressed by classical analysis and wicked but restrained problems (small
storms) controlled by \ac{incrementalism}.

@@

It is important to note that the same \ac{wicked-prob} is never faced twice, since each one is by definition, unique.
However, changes in technology, culture, and current affairs may render the current strategy insufficient and require
the process to start again. \Acp{wicked-prob} are like history: they don't repeat themselves, but they rhyme. Due to
changing circumstances, past solutions cannot be used in the future, but lessons learned from the past can be.

In the context of \ac{encryption} and \ac{EA}, this means that the outcome of \ac{the-cw1} doesn't hold precedential
power over the debate in the second. It means that re-raising questions about the role of technology plays in society is
legitimate. To follow this proposed strategy would mean that hard-line rhetoric doesn't help \cite{ruiz_there_2018}
\cite{geller_2019} but sincere appeals do \cite{abelson_2015} \cite{intl_2020} \cite{rozenshtein_2019}. Even more
helpful are collaborative efforts involving government, technical, and civil liberties representatives
\cite{committee_decrypting_2018} \cite{group_2019}. Specific proposals around which groups can center discussion,
whether they specify a particular form of \ac{EA} or perhaps especially if they don't, are also a necessary component
\cite{kerr_encryption_2017} \cite{wright_crypto_2018} \cite{phan_key_2017}.

In the remainder of this thesis, I apply this strategy by documenting the debate in depth in \mychap{chap-arguments} and
through creation of a threat model against which I analyze one specific proposal in \mychap{chap-threatmodel}.

>>>>

Cybersecurity law scholar Alan Rozenshtein argues at length for treating \ac{encryption} and \ac{EA} as a
\ac{wicked-prob} \cite{rozenshtein_wicked_2018}. He divides the root issues into three categories. First, there is
disagreement on what the goals should be (and even basic premises). Sides do not agree on how much to value competing
notions of security. Regarding the basic facts, sides do not agree on whether encryption is hiding so much evidence that
law enforcement is ``going dark,'' as one side puts it, or whether technological change overall has created a ``golden
age for surveillance,'' as their opponents argue. Second, information is ``uncertain and diffuse.'' Comprehensive data
regarding encryption's effect on investigations is unavailable. Although the consensus is that we are not presently
capable of acceptably secure \ac{EA}, that consensus could change, especially considering that \ac{EA} as a field is
under-researched. Third, that the problem cannot be definitively solved. Evolving values and technology mean that this
policy area is always up for renegotiation.

\Ac{encryption} technology is particularly sensitive to the irreversible effects of policy implementation. Technology
deployments have long tails and attackers have the ability to record and store data for later analysis. In one
investigation, Australian police cracked a cold case based on evidence acquired from a mobile device that they cracked
five years after it was seized \cite{evans_arrests_2020}. In this case, it was lawful authorities that benefitted from a
vulnerability. However, if miscalculated \ac{EA} mandates result in vulnerabilities such as this, attackers will
benefit, not just law enforcement.

@@

Reality must be accepted before it can be dealt with. \cite{baker_2019}. We have by now embraced the reality of
\acp{wicked-prob}. The next two sections investigate strategies for dealing with this reality.

@@

The \ac{classical-method} \cite{feeley_judicial_2000} (also known as ``the modern-classical model of planning''
\cite{rittel_dilemmas_1973}, ``the rational-comprehensive method'' \cite{lindblom_muddling_1959}, ``traditional policy
analysis'' \cite{rozenshtein_wicked_2018}, or ``linear thinking'' \cite{commission_tackling_2018}) has already been
introduced. It is the reason-based method that functions by setting goals, identifying problems, evaluating
alternatives, implementing solutions, and analyzing outcomes in order to correct errors. \myfig{fig-classical-method}
illustrates this approach in the context of encryption and \ac{EA}. It has a purely linear flow from problem to solution
except for the ``refinement'' step, in which the method analyzes outcomes and corrects errors. However, it is important
to note that refinement represents a reinforcement, as opposed to a reassessment, of the chosen solution.

@@

\Ac{incrementalism} is an intuitive and iterative approach posed as an alternative to the \ac{classical-method}.
\Ac{incrementalism} as a policymaking strategy is often referred to as ``\ac{muddling-through}'' from political
scientist Charles Lindblom's classic paper defining and defending the approach \cite{lindblom_muddling_1959}. Written
before Rittel developed the idea of ``\acp{wicked-prob},'' Lindblom nonetheless identified many of the same shortcomings
of the classical method and sought to formalize the process policymakers were already often using.

Lindblom's process of ``\ac{muddling-through}'' operates by taking successive steps chosen through comparative analysis.
The alternatives selected for comparison must be defined relative to the status quo and must be close enough to one
another that they can be analyzed on the margin. This is done due to (a) practical necessity, due to the inability to
predict policy outcomes, and (b) out of political realism, as non-incremental changes are usually politically impossible
to impose in a democratic system \cite{lindblom_muddling_1959}. The formality of the process varies; policymakers may
use this method consciously, with considerable comparative analysis, or unconsciously, led by intuition.
\myfig{fig-muddling-through} illustrates this method.

@@

\Ac{incrementalism} has several advantages over the \ac{classical-method} for handling \acp{wicked-prob}. It is rooted
in realism about the limits of rational analysis. It accepts that the problem will not be conclusively solved. Instead,
it emphasizes iteration: ``Policy is not made once and for all; it is made and re-made endlessly. Policy-making is a
process of successive approximation to some desired objectives in which what is desired itself continues to change under
reconsideration'' \cite{lindblom_muddling_1959}. Most importantly, it eschews the linear
problem-definition--alternatives-analysis steps out of respect that the problem definition is not self-contained.
Lindblom argues that policy ends and means are interlinked, eventually concluding:

@@

Despite its strengths, \ac{incrementalism} also has weaknesses in its ability to address \acp{wicked-prob}. Its main
weakness is the absence of high level strategic analysis. Incrementalism is incapable of drastic change, which is
sometimes necessary. By Lindblom's admission, it lacks a safeguard for consideration of all relevant values and may
``overlook excellent policies for no other reason than that they are not suggested by the chain of successive policy
steps leading up to the present'' \cite{lindblom_muddling_1959}. Analysis based only on the present status quo can
result in messy policy that pleases no one---``As Lindblom's sobriquet suggests, it often [leads] to a considerable
muddle'' \cite{feeley_judicial_2000}. Application of the \acl{CFAA} is one such muddle \cite{wolff_computer_2016}.

Unfortunately, one cannot simply add high level strategic analysis to the incrementalist method by including the past in
its analysis. \Ac{incrementalism} relies on simplifying analysis by limiting it to marginal differences to a given
baseline. If one tries to be a ``strategic incrementalist'' by looking into the past, they still have to choose a
baseline from which to perform analysis. This approach is susceptible to two weaknesses in baseline-based reasoning that
Rozenshtein describes in his analysis of \ac{EA} as a \ac{wicked-prob} \cite{rozenshtein_wicked_2018}. First, the choice
of baseline is arbitrary, yet heavily colors analysis:

@@

\Acp{wicked-prob} were earlier described as a tangle of contributing subproblems. Using this characterization, dealing
with a \ac{wicked-prob} requires disentangling the web, identifying the tame subproblems, and developing agreeable
strategies for the irreducibly wicked subproblems. Once that is done, we can rationally analyze and increment our way to
resolution. There is no handbook for how to do this, but several sources offer advice.

@@

Easy answers, or any solutions that artificially tame the problem, will not bring the matter under control. While by
definition there is no solution that will truly solve a \ac{wicked-prob}, easy answers deliberately emphasize one value
to the exclusion of others. Because they neglect the root issues, solutions based on easy answers produce unintended
consequences and chaos in those neglected areas \cite{commission_tackling_2018}.

@@

% TODO: Prof. Engelsma:
% - A big part of the "solution" is getting people together
% - My thesis seems aimed at tech people to get them to understand and judge threats
% - How can I take this accessible and bridge the gap for policymakers?

@@

The failures of the \ac{classical-method} and \ac{incrementalism} reveal that we must be able to think strategically
while respecting the non-linear nature of \acp{wicked-prob}. One must use the high level, holistic view of the classical
approach while intertwining the problem definition and analysis steps as in the incrementalist approach. In practice,
this means that the collective understanding of the problem and potential solutions must co-evolve. As Rittel puts it,
``The systems-approach `of the first generation' [i.e., classical analysis] is inadequate for dealing with
wicked-problems. Approaches of the `second generation' should be based on a model of planning as an argumentative
process in the course of which an image of the problem and of the solution emerges gradually among the participants, as
a product of incessant judgment, subjected to critical argument'' \cite{rittel_dilemmas_1973}.

@@

\Acp{wicked-prob}' potential solutions cannot be comprehensively evaluated before or even after implementation and each
action (or decision not to act) has irreversible effects. Proposals must therefore be agile. All decisions involve
unknowns, but risk- and uncertainty-management strategies can optimize the expected outcome and maximize the worst
outcome \cite{sunstein_beyond_2015}.

@@

Focusing on concrete proposals follows partially from the previous lesson---problem definition and analysis are combined
precisely because the problem definition depends on the nature of proposed solutions. But this advice deserves emphasis
for another reason: consensus is easier to achieve for concrete proposals. Debate in the abstract can rage endlessly, as
groups are bound to disagree due to their conflicting values and priorities. However, Lindblom writes encouragingly
about ``the ease with which individuals of different ideologies often can agree on concrete policy'' in an example about
congressional compromise. He goes on to say, ``Labor mediators report a similar phenomenon: the contestants cannot agree
on criteria for settling their disputes but can agree on specific proposals. Similarly, when one administrator's
objective turns out to be another's means, they often can agree on policy'' \cite{lindblom_muddling_1959}.

@@

The discussion above describes the inability of well-established methods of policymaking to address \acp{wicked-prob}
and lessons for shaping a better method. Here, I propose a modified \acs{OODAloop} as an alternative policymaking model.

@@

The \ac{OODAloop} serves well as a model for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It corresponds closely to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action; however, it also emphasizes \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking does not share the pace of real-time combat, this metaphor holds true in other ways. In
both cases, one faces an unpredictable opponent in a dynamic environment in which every action counts. We cannot
overpower \acp{wicked-prob} through force of reason, but perhaps we can through speed and agility.

The OODA Loop does need one modification in order to suit wicked problems. Because the problem definition step and
analysis step depend on one another, they must be joined. This is Rittel's ``argumentative process in the course of
which an image of the problem and of the solution emerges gradually'' \cite{rittel_dilemmas_1973}, illustrated in
\myfig{fig-policy-ooda-loop} as a cycle of ``collaborative debate'' between observation and orientation. The modified
\ac{OODAloop} incorporates each of the lessons from \mysec{sec-policy-lessons}.

@@

Traditional policymaking typically follows either (a) a rational approach rooted in the scientific method, aiming to be
thorough and complete, or (b) an intuitional approach rooted in evolutionary trial and error, humbly aiming only to take
steps in the right direction. Both approaches have strengths, but neither is suited to the complex and controversial
nature of \acp{wicked-prob}. The strategy proposed here relies on the goodwill participation of all parties who engage
in ongoing research and debate that rejects easy answers, encourages flexible risk-based solutions, and crystallizes
discussion around specific proposals. The result of a single iteration is a bit more clarity and a small step forward.
The result of many iterations is the breakdown of the problem into subproblems---some tame and inevitably some still
wicked. The tame subproblems can be addressed with the \ac{classical-method}, and the wicked subproblems, by now
restrained under a sound and agreeable strategy, can be addressed with \ac{incrementalism}.

This process is demonstrated in \myfig{fig-policy-ooda-process}. An out-of-control problem (represented by the large
storm) is confronted in this diagram. Several iterations of the \ac{OODAloop} gradually diminish its size. This is
achieved by spinning out tame problems (represented by puzzle pieces) which are addressed with classical analysis and
wicked but restrained problems (represented by small storms) which are controlled by \ac{incrementalism}.

@@

It is important to note that the same \ac{wicked-prob} is never faced twice, since each one is by definition, unique.
However, changes in technology, culture, and current affairs may render the current strategy insufficient and require
the process to start again. It has been said that history does not repeat itself, but it rhymes. \Acp{wicked-prob} are
the same. Past solutions cannot be used in the future, but lessons learned can be.

In the context of \ac{encryption} and \ac{EA}, this means that the outcome of \ac{the-cw1} doesn't hold precedential
power over the debate in the second. It means that it is legitimate to re-raise questions about the role technology
plays in society. Hard-line rhetoric doesn't help \cite{ruiz_there_2018} \cite{geller_2019}, but sincere appeals do
\cite{abelson_2015} \cite{intl_2020} \cite{rozenshtein_2019}. Collaborative efforts involving government, technical, and
civil liberties representatives are even better \cite{committee_decrypting_2018} \cite{group_2019}. Specific proposals
around which groups can center discussion are also necessary. This is true whether they specify a particular form of
\ac{EA} or (perhaps especially) if they offer an alternative \cite{kerr_encryption_2017} \cite{wright_crypto_2018}
\cite{phan_key_2017}.

I apply this strategy in the remainder of the thesis. \mychap{chap-arguments} documents the debate in depth and
\mychap{chap-threatmodel} defines a threat model against which I analyze a specific \ac{EA} proposal.

### 2020-12-11 Thesis-Chapter4-Tools.tex
Editorial improvements

Encryption policy arguments and \acl{EA} threat models are complex. \Acp{argmap} and \aclp{DFD} two methodological tools
to structure analysis and reduce complexity. This chapter introduces these tools and their syntax as used in
\mychap{chap-arguments} and \mychap{chap-threatmodel}.

@@

The arguments used in the \ac{EA} debate are diverse and complex. Therefore, in order to advance the \ac{EA} discussion,
it is necessary to organize the many different arguments in a cohesive manner. This thesis uses \acp{argmap} to do so.
\Acp{argmap} are graphical representations of the logical structures and relationships between statements, premises, and
conclusions. \Acp{argmap} are an outgrowth of the same research by Horst Rittel that originated the idea of
\acp{wicked-prob}. Though formal research on the technique is sparse, \acp{argmap} have proven helpful in simplifying
complex arguments around \acp{wicked-prob} \cite{renton_2007} and in facilitating debate. This is because they slow down
discussion, depersonalize conflict, and lend structure and rhythm to meetings \cite{dutoit_hypermedia_2006}. They are
therefore useful as a tool for conducting the collaborative debate that helps problem-solvers with disparate views
narrow in on a problem definition and concrete proposals on which they can agree.

In 1970 Rittel's research group developed \acp{IBIS} to break down \acp{wicked-prob} and document the reasoned
approaches that go into solving them \cite{kunz_issues_1970}. Interest in \ac{IBIS} has waxed and waned. Some software
tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006} tools designed to produce graphical representations. Argdown is a recent tool that
generates \acp{argmap} from structures specified in a Markdown-based language \cite{voigt_argdown_2018}. Argdown is used
in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA} debate.

\myfig{fig-args-key} shows the basic structure of arguments. Statements are positions, values, and assertions. The
``Proposals,'' ``Statements,'' ``Fallacies,'' and ``Values'' in the figure are classes of statements in this sense. The
color of a statement's border indicates the class to which it belongs. Arguments are premise-conclusion structures that
relate to statements. Arguments as classified as ``anti-EA,'' ``pro-EA,'' ``neutral,'' or ``fallacious.'' The color of
an argument's solid background indicates the class to which it belongs. Statements and arguments may support, attack, or
undercut one another. Supporting relationships have green arrows; attacking, red; and undercutting, purple.

@@

Threat modeling is an important step in analyzing the security at the systems level. Models abstract away fine details
and focus on the architecture, processes, and dataflows in a system. Models assist in the understanding of current
systems and the prevention of problems in new systems, both of which are important when facing the prospect of designing
an \ac{EA} mechanism built on top of a complex and aging technology stack.

@@

\Acp{DFD} were designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and external
entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data flow, not
control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of primary
concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman key
exchange.

@@

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. \mychap{chap-threatmodel} includes \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

>>>>

Encryption policy arguments and \acl{EA} threat models are complex. \Acp{argmap} and \aclp{DFD} are two methodological
tools that can be used to structure analysis and manage complexity. This chapter introduces these tools and their
syntax, which will be used in \mychap{chap-arguments} and \mychap{chap-threatmodel}.

@@

In order to advance the \ac{EA} discussion, it is necessary to organize the many different arguments in a cohesive
manner. This thesis uses \acp{argmap} to do so. \Acp{argmap} are graphical representations of the logical structures and
relationships between statements, premises, and conclusions. They originated from the same research as the idea of
\acp{wicked-prob}. Though formal research on the technique is sparse, \acp{argmap} have proven helpful in simplifying
complex arguments regarding \acp{wicked-prob} \cite{renton_2007} and in facilitating debate. This is because they slow
down discussion, depersonalize conflict, and lend structure and rhythm to meetings \cite{dutoit_hypermedia_2006}. They
are therefore useful as a tool for conducting the \ac{OODAloop} model's ``collaborative debate'' step.

Argument mapping tools originated in 1970 with text-based \acp{IBIS} designed to break down \acp{wicked-prob} and
document the reasoned approaches that go into solving them \cite{kunz_issues_1970}. Interest in \acp{IBIS} has waxed and
waned. Some software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006}, which were designed to produce graphical argument representations. Argdown is a recent
tool that generates graphical \acp{argmap} from structures specified in a Markdown-based language
\cite{voigt_argdown_2018}. Argdown is used in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA}
debate.

\myfig{fig-args-key} shows the basic structure of arguments. Statements can take the form of positions, values, and
assertions. The ``Proposals,'' ``Statements,'' ``Fallacies,'' and ``Values'' in the figure are classes of statements in
this sense. The color of a statement's border indicates the class to which it belongs. Arguments are premise-conclusion
structures that relate to statements; they are classified as ``anti-EA,'' ``pro-EA,'' ``neutral,'' or ``fallacious.'' An
argument's class is distinguished by the color of its solid background. Statements and arguments may support, attack, or
undercut one another. Green arrows represent supporting relationships; red arrows, attacking; and purple arrows,
undercutting.

@@

Threat modeling is an important step in analyzing the security at the systems level. Models abstract away fine details
and focus on the architecture, processes, and dataflows in a system. They assist in the understanding of current systems
and the prevention of problems in new systems, both of which are important when facing the prospect of designing an
\ac{EA} mechanism built on top of a complex and aging technology stack.

@@

\Acp{DFD} were designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and external
entities. \Acp{DFD} are well-suited for threat modeling because security vulnerabilities tend to follow data flow, not
control flow \cite{shostack_threat_2014}. They are particularly well-suited for \ac{EA}, as data privacy is of primary
concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman key
exchange.

@@

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
diagram. \myfig{fig-dfd-key} contains the full set of symbols. \mychap{chap-threatmodel} includes \acp{DFD} in this
style to analyze threats that EA would introduce.
